Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-22 doc/asplos13/relatedwork.tex
more todos

\paragraph{Comparable frameworks}
Distributed graph processing frameworks like Pregel \cite{pregel:2010} and
Distributed GraphLab \cite{distgraphlab:vldb12} share similar goals. Pregel
adopts a bulk-synchronous parallel (BSP) execution model, which makes it
inefficient on workloads that could prioritize vertices. GraphLab, on the
other hand, schedules vertex computations individually, allowing
prioritization, which gives faster convergence in a variety of iterative
algorithms.\TODO{GraphLab is not general. Myers will expand on that here. Make
a strong point about generality.} Grappa also supports dynamic parallelism
with asynchronous execution, but parallelism is expressed as tasks or loop
iterations.

>>>>

\paragraph{Comparable frameworks}
Distributed graph processing frameworks like Pregel \cite{pregel:2010} and
Distributed GraphLab \cite{distgraphlab:vldb12} share similar goals. Pregel
adopts a bulk-synchronous parallel (BSP) execution model, which makes it
inefficient on workloads that could prioritize vertices. GraphLab, on the
other hand, schedules vertex computations individually, allowing
prioritization, which gives faster convergence in a variety of iterative
algorithms.\TODO{GraphLab is not general. Myers will expand on that here. Make
a strong point about generality.} Grappa also supports dynamic parallelism
with asynchronous execution, but parallelism is expressed as tasks or loop
iterations.\TODO{Should RAMcloud go here?}.
